---
title: Sample Section
subtitle: stuff here 
author: Jesus G
date: today
toc: true 

---

```{r}
#| message: false
#| echo: false
#| warning: false

library(tidyverse)
```


# Section 1: Some stuff here  

Ploting some data for funzies. And playing around with Quarto website capabilities. 


## Sub-section of 1: some smaller stuff here 

Some other data stuff. 

### Header of smalles items

blah blah here 

- bulleted item 1 
- the second whatever 

1. blah blah one 
2. blah two 
3. blah three

text can be **bold** or _italics_, or ~~strikethrough~~

my website is <https://rsm-jeg031.github.io/> or [here](https://rsm-jeg031.github.io/)

# Section 2: some math stuff 

if you want inline math $y = mx + b$ 

$$
\int_o^1 x^2 dx = \frac{1}{3}
$$

some latex math below 

\begin{align}
y &= a(b+c) \\
  &= ab + ac
\end{align}


# Section 3: code sytax for neat looking pages 😎

you can do inline code like so `sqrt(2)` then add the language prior to the line of code to get the result `r sqrt(2)`


**show the code, hide results**

```{r}
#| results: hide

data(mtcars)
cor(mtcars$mpg, mtcars$wt)
```

**show the results, hide the code**

```{r}
#| echo: false 

data(mtcars)
cor(mtcars$mpg, mtcars$wt)
```

# Section 4: plots

```{r}
library(ggplot2)
```

```{r}
#| fig-height: 4
#| fig-width: 4
#| fig-align: center
mtcars %>%
    ggplot(aes(mpg, wt)) +
    geom_point(col="dodgerblue4", size=2)
```

# Section 5: Tables 


```{r}
mtcars[1:5,]
```


```{r}
knitr::kable(mtcars[1:5,])
```


# Bonus stuff: 

:::{.callout-note collapse="true"}
## note title

some dash  

```{r}
#| fig-height: 4
#| fig-width: 4
#| fig-align: center
#| echo: false
p <- mtcars %>%
    ggplot(aes(mpg, wt)) +
    geom_point(col="dodgerblue4", size=2)
```

:::


A tabset panel

:::{.panel-tabset}

## Jesus Tab

```{r}
p
```

## Brian Tab 

```{r}
#| echo: false
p + geom_smooth(method="lm", se=FALSE)
```

:::




